\documentclass[11pt]{article}


\usepackage{soul}
\usepackage[T1]{fontenc}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{subfloat}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{verbatim, rotating, paralist}
\usepackage{enumerate}


\usepackage{natbib}
\usepackage{pdfsync}
\usepackage{latexsym}
\usepackage{amsthm}
\usepackage{mathabx}


\usepackage{stmaryrd}
\usepackage{mathrsfs}
\usepackage{dsfont}
\usepackage{parskip}
\usepackage{anysize, indentfirst, setspace}
\usepackage[right=1.7cm, left=1.7cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{epigraph}
\usepackage{appendix}
\usepackage{fancyhdr}


\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}


\pagestyle{myheadings}
\markright{ }


% header
\pagestyle{fancyplain}
\rhead{\hfill \small \emph{Adriane Fresh --- Top 10 Publications --- Page \thepage}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}










%%  BEGIN DOCUMENT %%
%%--------------------------------%%

\begin{document}

\singlespacing
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}


% \thispagestyle{empty}



%%  HEADER  %%
%%----------------%%


\noindent \large{\textbf{\so{Top 10 Publications}}} \\ \normalsize
\noindent Adriane Fresh \\
\noindent Re-appointment Review, AY2022-2023  \\

\vspace*{.2in}

\begin{enumerate}
    \item Eubank, Nicholas and \textbf{Adriane Fresh} (2022). ``Enfranchisement and Incarceration after the Voting Rights Act.'' \underline{\emph{American Political Science Review}} Vol. 116 No. 3. \\ DOI: \url{https://doi.org/10.1017/S0003055421001337} \\

    \item \textbf{Fresh, Adriane} (2018). ``The Effect of Section 5 Coverage on Enfranchisement: Evidence from North Carolina.'' \underline{\emph{Journal of Politics}} Vol. 80 No. 2.\\ DOI: \url{https://doi.org/10.1086/697592} \\


    \item Clinton, Joshua D., Nicholas Eubank, \textbf{Adriane Fresh}, Michael Shepherd (2021). ``The Politics of Locating Polling Places:  Race and Partisanship in North Carolina Election Administration, 2008-2016.''\underline{\emph{Election Law Journal}}  Vol. 20 No. 2. \\ DOI: \url{https://doi.org/10.1089/elj.2019.0602} \\

    \item Clinton, Joshua D., Nicholas Eubank, \textbf{Adriane Fresh}, Michael Shepherd (2021). ``Polling Place Changes and Political Participation: Evidence from North Carolina Presidential Elections, 2008-2012.'' \underline{\emph{Political Science Research and Methods}} Vol. 9 No. 4. \\ DOI: \url{https://doi.org/10.1017/psrm.2020.43}
\end{enumerate}





\end{document}
